Dependent Object Types

### 2012-08-06 article.tex
grammar

Notice that $d$ has type $\Bot$ if the cast on $b$ is ignored. This
example didn't typecheck initially because the path-equality
provisions only applied when objects are in the store, so the
application was not well-typed. But if we started preservation in a store
which has $a$, $b$, $c$ and $d$ then the application type-checked,
because, through one of the path-equality provision, we could find that
the type of $d$ was a subtype of $\Bot$. Now, of course, when we got to
$d.\mathit{foo}$, reduction failed.

>>>>

Notice that $d$ has type $\Bot$ if the cast on $b$ is ignored. This
example didn't typecheck initially because the path-equality
provisions only applied when objects are in the store, so the
application was not well-typed. But if we started preservation in a store
which had $a$, $b$, $c$ and $d$ then the application type-checked,
because, through one of the path-equality provision, we could find that
the type of $d$ was a subtype of $\Bot$. Now, of course, when we got to
$d.\mathit{foo}$, reduction failed.
